---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, 
        pillar.bold = TRUE, 
        pillar.min_chars = 25, 
        pillar.min_title_chars = 25,
        dplyr.summarise.inform = FALSE)

```

# fpscrapr

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/fpscrapr)](https://CRAN.R-project.org/package=fpscrapr)

<!-- badges: end -->

Helps scrape FantasyPros.com by handling rate-limiting/caching/parsing and returning tidy dataframes which can be easily connected to other data sources.

## Installation

Install the development version from GitHub with:

```{r eval = FALSE}
 
 # install.packages('remotes')
 
 remotes::install_github("dynastyprocess/fpscrapr")
```

## Example

All `fpscrapr` functions start with fp.

The fp_rankings function retrieves fantasy ranks from fantasypros.com and right now is only tested with NFL.

```{r example}
library(fpscrapr)

fp_rankings(page = "consensus-cheatsheets", sport = "nfl")

fp_rankings(page = "ros-overall", sport = "nhl")

```
